GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-22 paper/kbanotebook2013/content/implementation.tex

We use Wikipedia API to get some aliases automatically. This is done by retrieving backlink references (redirects of a wiki entity). Unfortunately this is not good enough and to enhance recall we need more aliases. To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity. Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities. To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -> Gates, Bill.

@@

Next we will explain the patterns with more details. Lets’s first look at one example of the first kind of patterns. For slot FounderOf, we have this pattern: <PER, FounderOf, founder, right, ORG>. PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot. founder is the ankor word we are trying to match in the sentence text; right means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.

Here is an example for the second type: <PER, AwardsWon, awarded, right, NP>, NP meaning noun phrase. This pattern can be interpreted as that we are looking for a noun phrase after the “awarded” since that noun phrase could possibly represent an award. Since titles and awards are usually not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the noun phrases.

Another example for the third type: <PER, DateOfDeath, died, right, last night>. In this pattern, “last night” means we are looking for exactly the phrase “last night” to the right of “died”. This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like “last night” as a DATE entity.

>>>>

We use Wikipedia API to get some aliases automatically. This is done by retrieving backlink references (redirects of a wiki entity). Unfortunately this is not good enough and to enhance recall we need more aliases. To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity. Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities. To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -\textgreater Gates, Bill.

@@

Next we will explain the patterns with more details. Lets’s first look at one example of the first kind of patterns. For slot FounderOf, we have this pattern: \textless PER, FounderOf, founder, right, ORG\textgreater. PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot. founder is the ankor word we are trying to match in the sentence text; right means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.

Here is an example for the second type: \textless PER, AwardsWon, awarded, right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted as that we are looking for a noun phrase after the “awarded” since that noun phrase could possibly represent an award. Since titles and awards are usually not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the noun phrases.

Another example for the third type: \textless PER, DateOfDeath, died, right, last night\textgreater. In this pattern, “last night” means we are looking for exactly the phrase “last night” to the right of “died”. This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like “last night” as a DATE entity.
